Model

### 2019-08-27 stats/model.Rmd
add 2 more model runs

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 10,
#   cores = 10,
#   inference_opts = list(method = "incrementalMH",
#                         samples = 4000,
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 500)
# )

# load this for model parameters
sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# # load this for model parameters with wider prior on so_slope (0:3)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
# 
# # load this for model parameters with even wider prior on so_slope (0:4)
# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

#saveRDS(sem_know_model, "../saves/sem_know_new_model_3.rds")

>>>>

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 10,
  cores = 10,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 500)
)

# load this for model parameters with so_slope (0:2)
#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

# # load this for model parameters with wider prior on so_slope (0:3)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")

# # load this for model parameters with wider prior on so_slope (0:3) (second run)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2_2.rds")%>%
#   filter(Chain != 2)

# # load this for model parameters with even wider prior on so_slope (0:4)
# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

# # load this for model parameters with wider prior on so_slope (0:4), so_int, as well as on global paramters of semantic knowledge
sem_know_model <- readRDS("../saves/sem_know_new_model_4.rds")%>%
  filter(Chain !=9)

#saveRDS(sem_know_model, "../saves/sem_know_new_model_4.rds")
